Reviewer comments from PeerJ

### 2015-03-02 PeerJResponse.tex
Edits
edits to response, text, for reviewer 2

\lev{i will check this but i believe mexicana not included because we didn't discuss them with respect to the high frequency stuff. I do not have arcgis any more and would prefer to not completely redo this figure. I am happy to put names on pops though. I don't understand comments about 'left hand side' stuff. Yes, some of the populations are close together when you are that zoomed out on a map. There is no way to have them not all coming from the same place in some cases unless the map was so gigantic to take up an entire page.}

@@

>>>>

@@

\res{We only included \emph{parviglumis} in this graph because we wanted to highlight the difference in frequency within the Jalisco region, even between populations that are geographically very close to each other. Reviewer 2 is correct in stating that there is a large difference in the frequency of the \emph{Hopscotch} allele within 25 miles. Previous studies by \citet{Hufford2010; Moeller01072007} have shown that populations in this area are highly differentiated and likely have different evolutionary histories.}

\res{We have edited the figure to include the names of the four populations in the Jalisco region that we intend to highlight: La Mesa, San Lorenzo, Ejulta A, and Ejutla B.}
